<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Knitr and ReportingTools}
-->

Knitr and ReportingTools
===============================================

       
We can use knitr and ReportingTools together, as shown in this very simple example from our basic vignette.  To see the output of this vignette, simply run the knitr function knit2html('knitr.Rmd', output=".reports/output.html").  

 **Note: the output html file must be in the directory indicated by the location argument.** If this is not the case the ReportingTools functionality will break, and ReportingTools has no way of detecting that this is the case because the final HTML file is written by knitr, not ReportingTools. If not specified via the output argument, knitr will write the destination file within the current working directory.  When calling knit2html, the output should be in the same directory as the reportDirectory specified below (e.g., "./reports").

```{r message=FALSE, results="asis"}
my.df <- data.frame(EGID = c("103", "104", "105", "106", "107"),
                    RPKM = c(4, 5, 3, 100, 75),
                    DE = c("Yes", "Yes", "No", "No", "No"))

library(ReportingTools)
```
We now can publish our data frame as table through the use of the knitrHandlers.  When using knitrHandlers we must specify the destination location as an argument either to the knitrHandlers constructor function directly or as an additional argument to HTMLReport when knitrHandlers is specified  in the handlers argument.

We do not call finish since we will still add output to our knitr report.

```{r results="asis"}
library(XML)
htmlRep <- HTMLReport(shortName = "knitrReport",
    reportDirectory = "./reports", handlers=knitrHandlers, location="./reports/knitrTest.html")
#publish(my.df, htmlRep)
htmlRep[["mydf"]]<-my.df  ##this line is equivalent to the line above
```
Thus we are able to include tables generated by ReportingTools based directly within knitr documents.

Now we will try to put in an image:

```{r results = "asis"}
library(lattice)
set.seed(123)
htmlRep[["pic"]] = xyplot(y~x, data = data.frame(y=rnorm(25), x=rnorm(25)))
##We could also add a picture like this:
y <- rnorm(500)
pic2<-histogram(y, main="Sample of 500 observations from a Normal (0,1)")
publish(pic2, htmlRep)
```

As we have seen, using ReportingTools in conjunction with knitr is as easy as selecting a different set of ReportHandlers (in this case those generated by the knitrHandlers constructor function) and ensuring that the location of the final HTML file matches (up to the directory) that specified by the location field of that ReportHandlers object.

This allows us to create rich knitr-based reports and vignettes while leveraging the power of ReportingTools to format and display generated R objects.

