<style>
p {font-size:large}
</style>

For this vignette we will examine the ALL dataset.  First we load our ReportingTools  package and the data.  This dataset is from a clinical trial in acute lymphoblastic leukemia (ALL) and  is available from Bioconductor.  

```{r message=FALSE, output="hide"}
library(ReportingTools)
library(ALL)
library(hgu95av2.db)
library(genefilter)
library(GOstats)
library(limma)
library(GSEAlm)
library(GSEABase)
data(ALL)

ALL <- ALL[, ALL$mol.biol %in% c('NEG','BCR/ABL') &
    !is.na(ALL$sex)]
ALL$mol.biol <- factor(ALL$mol.biol, 
    levels = c('NEG', 'BCR/ABL'))
ALL <- featureFilter(ALL)
```
First we create a eBayes fit (but don't publish it):

```{r results="asis"}
model <- model.matrix(~mol.biol+sex, ALL)
fit <- eBayes(lmFit(ALL, model))
myrep = htmlReportRef(reportDirectory = "./",shortName="bigtest", handlers = ReportingTools:::knitrHandlers)

#publish(fit, myrep, eSet=ALL, factor=ALL$mol.biol, coef=2, n=100)
```

Next we publish some hyperGTest results:

```{r results="asis"}
tt <- topTable(fit, coef = 2, n = 100)
selectedIDs <- unlist(mget(tt$ID, hgu95av2ENTREZID))
universeIDs <- unlist(mget(featureNames(ALL), hgu95av2ENTREZID))
goParams <- new("GOHyperGParams", 
    geneIds = selectedIDs, 
    universeGeneIds = universeIDs, 
    annotation = annotation(ALL), 
    ontology = "BP", 
    pvalueCutoff = 0.01,
    conditional = TRUE, 
    testDirection = "over")
goResults <- hyperGTest(goParams)

publish(goResults, myrep, selectedIDs=selectedIDs, annotation.db="org.Hs.eg")
```

But I really like the number 5, so lets try publishing our GO results again...:

```{r results="asis"}
fiveCol = function(df, ...) cbind(df, fives=5)
publish(goResults, myrep, selectedIDs=selectedIDs, annotation.db="org.Hs.eg", .addColumns = fiveCol)
```

But now all my links and images are broken/gone! I've been thinking about the optimal interface to specify that you want to modify the default report df instead of the "core" one, but for now we can do this:

```{r results="asis"}
publish(goResults, myrep, selectedIDs=selectedIDs, annotation.db="org.Hs.eg", .addColumns = list(addReportColumns, fiveCol))
```

But now I'm tired of this same old table, lets change it up!

```{r results="asis"}
sillyHTML = function(obj,...) newXMLNode("h2", paste("What is this text doing here?! I'm supposed to be publishing an object of class ", class(obj), "! This was probably not a good use of .toHTML customization.", sep=""))
publish(goResults, myrep, selectedIDs=selectedIDs, annotation.db="org.Hs.eg", .toHTML = sillyHTML)
```

That was probably overkill, Maybe we want a table, but we don't agree with some things in the default toReportDF method ...

```{r results="asis"}
sillyDF = function(...) data.frame(x=rnorm(10), y = rnorm(10, 4))
publish(goResults, myrep, selectedIDs=selectedIDs, annotation.db="org.Hs.eg", .toDF = sillyDF, .addColumns = fiveCol)
```
